Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-01-23 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
change filepath 2019

write.csv(
   Herm_17_m,
   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2019/Hermitage/Hermitage_19_mean.csv",
   row.names = FALSE
)

>>>>

write.csv(
   Herm_17_m,
   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2019/Hermitage_19_mean.csv",
   row.names = FALSE
)
